B_pilot_2

### 2018-08-31 experiments/B_pilot_2/B_pilot_2.Rmd
mvd writeup contents up

```{r pander, echo=FALSE, cache=FALSE, message=FALSE}
library(knitr)
library(tidyverse)
library(broom)
library(broom.mixed)
library(lme4)
library(lmerTest)
library(dotwhisker)
library(kableExtra)
library(LMERConvenienceFunctions)
library(data.table)
library(grid)
library(gridExtra)
source('summarySEwithin2.R')
source("B_pilot_2_functions/pretty_coef_table.R")
```

@@

```{r rawdata, cache=FALSE}
rawdata <- read.table('data.txt', sep=' ')
rawdata %>% head() 
```

>>>>

```{r pander, echo=FALSE, cache=FALSE, message=FALSE}
library(knitr)
library(tidyverse)
library(broom)
library(broom.mixed)
library(lme4)
library(lmerTest)
library(dotwhisker)
library(kableExtra)
library(LMERConvenienceFunctions)
library(data.table)
library(grid)
library(gridExtra)
source("B_pilot_2_functions/summarySEwithin2.R")
source("B_pilot_2_functions/pretty_coef_table.R")
```

@@

```{r rawdata, cache=FALSE, comment=NA}
rawdata <- read.table('data.txt', sep=' ')
rawdata %>% head() 
```
